
\documentclass[onecolumn, a4paper, 12pt]{article}

\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{amsmath}
\usepackage{rotating}   % 用于竖排文字
\usepackage{float}      % 用于强制固定图片位置
\usepackage[margin=2.5cm]{geometry}
\usepackage{lipsum}     % 假文生成

\title{ Test Paper DOC_003: Persistent web-enabled approach }
\author{ Kevin White }
\date{ 1985-07-24 }

\begin{document}

\maketitle

\begin{abstract}
This is a generated test document (ID: DOC_003) to verify PDF parsing capabilities. 
Layout Mode: \textbf{ onecolumn }. 
Features included: Vertical Text, Tables, Lists, Formulas, and Images.
\end{abstract}

% --- 随机章节生成 ---

\section{ Enable Visionary Synergies }
Power increase three international seven. What summer sit executive nor exactly ok. Seat car church produce. Media if myself actually from shake explain standard. Right political commercial project quality be need. Program behind to organization leg recognize.

% [特征1] 列表测试

\subsection*{Structured List}
\begin{itemize}
    
    \item \textbf{Item 1:} poor
        
    
    \item \textbf{Item 2:} decision
        
        \begin{itemize} 
            \item Nested item for structural depth test.
        \end{itemize}
        
    
    \item \textbf{Item 3:} building
        
    
\end{itemize}


% [特征2] 竖排文字测试 (Hard Case)

\vspace{0.5cm}
\noindent
\begin{minipage}{0.8\linewidth}
    \textbf{[Normal Text Stream]} The following block tests the parser's ability to handle mixed text orientation.
\end{minipage}%
\hfill
\begin{minipage}{0.15\linewidth}
    \rotatebox{90}{\textbf{>>> Vertical Text Zone (DOC_003) <<<}}
\end{minipage}
\vspace{0.5cm}


% [特征3] 数学公式


% [特征4] 表格 (随机列数)


% [特征5] 图片



\section{ Innovate Back-End Vortals }
Least state approach. Hour let set appear. Wish but international really tax receive continue. Defense difference knowledge debate bill deal through. Ever sea wear course check group up. Design wall sell star imagine. Shoulder positive or task difference project few finish. Here surface head former. Speech whom oil positive.

% [特征1] 列表测试

\subsection*{Structured List}
\begin{itemize}
    
    \item \textbf{Item 1:} reflect
        
    
    \item \textbf{Item 2:} wrong
        
        \begin{itemize} 
            \item Nested item for structural depth test.
        \end{itemize}
        
    
    \item \textbf{Item 3:} rise
        
    
\end{itemize}


% [特征2] 竖排文字测试 (Hard Case)


% [特征3] 数学公式

\begin{equation}
    f(x) = \alpha \cdot x^2 + \sum_{i=0}^{\infty} \beta_i
\end{equation}


% [特征4] 表格 (随机列数)

\begin{table}[H]
    \centering
    \caption{ Data analysis for section 2 }
    \begin{tabular}{ l c r }
        \toprule
        Item & Count & Ratio \\
        \midrule
        
        Row 1 & 93 & 0.54 \\
        
        Row 2 & 33 & 0.77 \\
        
        Row 3 & 59 & 0.46 \\
        
        \bottomrule
    \end{tabular}
\end{table}


% [特征5] 图片




\end{document}